---
title: "Project8"
output: html_document
---


#Preliminary
##load the packages
```{r,messages=F}
require(caret)
require(dplyr)
require(DMwR2)
require(rpart)
require(randomForest)

```


##Load the data
```{r}
training<-read.csv("training.csv",stringsAsFactors = T)
testing<-read.csv("testing.csv",stringsAsFactors = T)
```

#Preprocess
1) Dealing with Missing values and blank 
```{r}
##For training data
training$classe<-factor(training$classe)
f<-function(x){sum(is.na(x)|x=="")}
NAs<-apply(training,2,f)
NABlank<-as.data.frame(NAs)
colNAblank<-which(NABlank$NAs==14261)
data<-training[,-colNAblank]
cleandata<-centralImputation(data)
##For testing data
NAs2<-apply(testing,2,f)
NABlank2<-as.data.frame(NAs)
colNAblank2<-which(NABlank$NAs==14261)
data2<-testing[,-colNAblank2]
testData<-centralImputation(data2)

```


2) - exclude informational variables
```{r}
candidate<-grepl("belt|[^(fore)]arm|dumbbell|forearm",names(cleandata))
##The resulte indicates that Column 1-7 are information variables and are excluded,
##Column 37  is a factor with more than 52 levels which indicattes it is a informational variable too.
modeldata<-cleandata[,-c(1:7)]
modeldata<-modeldata[,-37]

testData<-testData[,-c(1:7)]
testData<-testData[,-37]

```


3) drop levels of the independent variable
```{r, message = F}
modeldata<-modeldata%>%
  filter(classe %in% c("A","B","C","D"))
modeldata$classe<-droplevels(modeldata$classe)
```


4) Splitting the training data
```{r}
x<-createDataPartition(modeldata$classe,p=0.6,list=F)
trainData<-modeldata[x,]
validateData<-modeldata[-x,]
```

#Building the model 
##Parallel Computing
```{r}
require(parallel)
require(doParallel)
cluster<- makeCluster(detectCores()-1)
registerDoParallel(cluster)

```

##Building the model with Random Forest, 5-fold cross valudation
```{r}
ctrl<-trainControl(method = "cv", number = 5) 
fit_RF<- train(classe~ ., data = trainData, method = "rf", trControl = ctrl)

```


##Making predictions on the validation data
```{r}
p_RF<-predict(fit_RF,validateData,type="raw")
```

##Model Evaluation on the validation data
```{r}
confusionMatrix(p_RF, validateData$classe)
```


#Making Prediction on the test data
```{r}
ptest_RF<-predict(fit_RF,testData,type="raw")
ptest_RF
```










